---
title: "Group 4 Project 1: Interim Report"
author: Paul Anderson, Michael Barton, Kevin Kincaid
format: pdf
---

```{r}
#| label: document settings
#| include: false
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE)
```

```{r}
#| label: load in packages
#| include: false
library(tidyverse)
```

## Introduction: Can income be predicted from selected ACS Data

In this interim report, we use individual-level data for Oregon residents from the 2020–2024 American Community Survey (ACS) 5-year Public Use Microdata Sample (1). Exploratory analyses were conducted to evaluate each proposed research question, leading us to focus on the question, “What factors are most impactful in predicting income?” Exploratory analysis is used to assess the distribution of income and its relationships with key demographic and socioeconomic variables. Based on the observed patterns, a full multiple linear regression model is specified, and ANOVA-based comparisons are used to identify an appropriate reduced model and evaluate its performance. We then discuss model justification and potential next steps.

```{r}
#| label: install-deps
#| include: false
# reticulate::virtualenv_create("r-reticulate")
# reticulate::virtualenv_install("r-reticulate", c("requests", "pandas"))
```

```{r}
#| label: add-reticulate
#| include: false
# file.edit("~/.Rprofile")
# add in this 
# Sys.setenv(RETICULATE_PYTHON_ENV = "r-reticulate")
```

```{r}
#| label: optional-pyrestart
#| include: false
# run the following restart the python session if needed
# reticulate::py_run_string("import gc; gc.collect()")
```

```{python}
#| label: fetch-metadata
#| include: false # removed from our output
#| cache: false

import requests
import json
from pathlib import Path

METADATA_PATH = Path("data/pums_variables_metadata.json")

variables = [ # added POBP, JWTRNS, NRC
    "WAGP", "PINCP", "PERNP", "POVPIP", "HICOV", "ESR",
    "AGEP", "SEX", "RAC1P", "HISP", "CIT", "YOEP", "MAR", "RELSHIPP",
    "POBP", "SCHL", "FOD1P", "SCH", "COW", "WKHP", "WKWN", "NAICSP", "OCCP", 
    "WRK", "JWMNP", "JWTRNS", "PUMA", "MIG", "MIGSP", "POWSP",
    "DIS", "DPHY", "DREM", "DEAR", "DEYE","HINCP", "HHT", "TEN", "VEH",
    "NRC", "RETP", "SSP", "SSIP", "PAP", "SEMP",
    "PWGTP", "ADJINC",
]

BASE_URL = "https://api.census.gov/data/2024/acs/acs1/pums/variables/{}.json"

if METADATA_PATH.exists():
    print(f"Loading metadata from cache: {METADATA_PATH}")
    with open(METADATA_PATH) as f:
        metadata = json.load(f)
else:
    print("Fetching variable metadata from Census API...")
    METADATA_PATH.parent.mkdir(parents=True, exist_ok=True)
    metadata = {}

    for var in variables:
        response = requests.get(BASE_URL.format(var), timeout=30)
        if response.status_code == 200:
            metadata[var] = response.json()
            print(f"  OK: {var}")
        else:
            print(f"  FAILED: {var} — {response.status_code}")

    with open(METADATA_PATH, "w") as f:
        json.dump(metadata, f, indent=2)

    print(f"\nSaved metadata for {len(metadata)} variables to {METADATA_PATH}")

# Preview one variable
print(json.dumps(metadata.get("WAGP", {}), indent=2))
```

```{python}
#| label: fetch-pums
#| include: false
#| cache: false

# --- Scrub Start ---

import requests
import pandas as pd
from pathlib import Path

API_KEY = "a8f34453c39e419470f405353250f662a508d821"
YEAR = 2024
STATE = "41"
CACHE_PATH = Path("data/pums_oregon_2024.csv")

variables = [
    # Outcomes
    "WAGP", "PINCP", "PERNP", "POVPIP", "HICOV", "ESR",
    # Core demographics
    "AGEP", "SEX", "RAC1P", "HISP", "CIT", "YOEP", "MAR", "RELSHIPP",
    "POBP",                                                       # added POBP
    # Education
    "SCHL", "FOD1P", "SCH",
    # Labor market
    "COW", "WKHP", "WKWN", "NAICSP", "OCCP", "WRK", "JWMNP", "JWTRNS", # added
    # Geography
    "PUMA", "MIG", "MIGSP", "POWSP",
    # Disability & health
    "DIS", "DPHY", "DREM", "DEAR", "DEYE",
    # Household context
    "HINCP", "HHT", "TEN", "VEH", "NRC",                            # added NRC
    # Income components
    "RETP", "SSP", "SSIP", "PAP", "SEMP",
    # Weights & adjustments
    "PWGTP", "ADJINC","NP",
]

if CACHE_PATH.exists():
    print(f"Loading from local cache: {CACHE_PATH}")
    pums = pd.read_csv(CACHE_PATH, low_memory=False)
    print(f"Loaded: {len(pums):,} rows, {pums.shape[1]} columns")
else:
    print(f"Cache not found — fetching from Census API...")
    CACHE_PATH.parent.mkdir(parents=True, exist_ok=True)
    url = (
        f"https://api.census.gov/data/{YEAR}/acs/acs5/pums"
        f"?get={','.join(variables)}"
        f"&for=state:{STATE}"
        f"&key={API_KEY}"
    )
    response = requests.get(url, timeout=60)
    print(f"Status code: {response.status_code}")
    if response.status_code == 200:
        data = response.json()
        pums = pd.DataFrame(data[1:], columns=data[0])
        pums.to_csv(CACHE_PATH, index=False)
        print(f"Saved to {CACHE_PATH}: {len(pums):,} rows, {pums.shape[1]} columns")
    else:
        print(f"Error: {response.text[:500]}")
```

```{r}
#| label: load-pums
#| include: false

pums <- read_csv("data/pums_oregon_2024.csv", show_col_types = FALSE)

#glimpse(pums)
```

```{r}
#| label: scrub-pums
#| echo: false
#| cache: true

pums_clean <- pums |>

  # --- Remove group quarters records ---
  filter(HINCP != -60000) |>

  # --- Apply income adjustment factor ---
  mutate(
    across(c(WAGP, PINCP, PERNP, HINCP, RETP, SSP, SSIP, PAP, SEMP),
           ~ .x * ADJINC)
  ) |>

  # --- Recode all N/A sentinels to NA ---
  mutate(
    # Income vars: age-based N/A
    WAGP   = na_if(WAGP,  -1 * ADJINC),
    PERNP  = na_if(PERNP, -10001 * ADJINC),
    PINCP  = na_if(PINCP, -19999 * ADJINC),
    RETP   = na_if(RETP,  -1 * ADJINC),
    SSP    = na_if(SSP,   -1 * ADJINC),
    SSIP   = na_if(SSIP,  -1 * ADJINC),
    PAP    = na_if(PAP,   -1 * ADJINC),
    SEMP   = na_if(SEMP,  -10001 * ADJINC),
    # Labor market: 0 = N/A (under 16 or did not work)
    WKHP   = na_if(WKHP, 0),
    WKWN   = na_if(WKWN, 0),
    JWMNP  = na_if(JWMNP, 0),
    # Other sentinels
    POVPIP = na_if(POVPIP, -1),
    ESR    = na_if(ESR, 0),
    YOEP   = na_if(YOEP, 1937),
    HHT    = na_if(HHT, 0),
    TEN    = na_if(TEN, 0),
    VEH    = na_if(VEH, -1),
    NRC    = na_if(NRC, -1),
    DPHY   = na_if(DPHY, 0),
    DREM   = na_if(DREM, 0),
    NP     = na_if(NP, 0),
    # Labor class and work status: 0 = N/A
    COW    = na_if(COW, 0),
    WRK    = na_if(WRK, 0),
  ) |>

  # --- Recode binary vars to logical (1=Yes, 2=No) ---
  mutate(
    across(c(DPHY, DREM, DEAR, DEYE, DIS), ~ .x == 1),
    HICOV = HICOV == 1,
  ) |>

  # --- Recode categorical vars as factors with labels from metadata ---
  mutate(
    SEX = factor(SEX, levels = c(1, 2),
                 labels = c("Male", "Female")),

    RAC1P = factor(RAC1P, levels = 1:9,
                   labels = c("White alone", "Black or African American alone",
                              "American Indian alone", "Alaska Native alone",
                              "AIAN tribes specified", "Asian alone",
                              "Native Hawaiian and Other Pacific Islander alone",
                              "Some other race alone", "Two or More Races")),

    HISP_binary = factor(if_else(HISP == "01", "Not Hispanic", "Hispanic")),

    CIT = factor(CIT, levels = 1:5,
                 labels = c("Born in US", "Born in PR/territories",
                            "Born abroad of US citizen parent",
                            "Naturalized citizen", "Not a US citizen")),

    MAR = factor(MAR, levels = 1:5,
                 labels = c("Married", "Widowed", "Divorced",
                            "Separated", "Never married")),

    ESR = factor(ESR, levels = 1:6,
                 labels = c("Civilian employed at work",
                            "Civilian employed not at work",
                            "Unemployed",
                            "Armed Forces at work",
                            "Armed Forces not at work",
                            "Not in labor force")),

    SCH = factor(SCH, levels = 1:3,
                 labels = c("Not enrolled", "Public school", "Private school")),

    COW = factor(COW, levels = 1:9,
                 labels = c("Private for-profit", "Private nonprofit",
                            "Local govt", "State govt", "Federal govt",
                            "Self-emp incorporated", "Self-emp not incorporated",
                            "Working without pay", "Unemployed last 5 years")),

    MIG = factor(MIG, levels = 1:3,
                 labels = c("Same house", "Outside US", "Different house in US")),

    HHT = factor(HHT, levels = 1:7,
                 labels = c("Married couple household",
                            "Other family: male householder no spouse",
                            "Other family: female householder no spouse",
                            "Nonfamily: male householder living alone",
                            "Nonfamily: male householder not living alone",
                            "Nonfamily: female householder living alone",
                            "Nonfamily: female householder not living alone")),

    TEN = factor(TEN, levels = 1:4,
                 labels = c("Owned with mortgage", "Owned free and clear",
                            "Rented", "Occupied without payment")),

    WRK = factor(WRK, levels = 1:2,
                 labels = c("Worked last week", "Did not work last week")),

    JWTRNS = factor(JWTRNS, levels = 0:12,
                    labels = c("N/A", "Car truck or van", "Bus",
                               "Subway or elevated rail",
                               "Long-distance train or commuter rail",
                               "Light rail streetcar or trolley",
                               "Ferryboat", "Taxi or ride-hailing",
                               "Motorcycle", "Bicycle", "Walked",
                               "Worked from home", "Other method")),

    POBP_binary = factor(case_when(
      as.numeric(POBP) <= 56  ~ "Born in US",
      as.numeric(POBP) == 72  ~ "Born in PR/territories",
      TRUE                    ~ "Foreign born"
    )),
  ) |>

  # --- Drop redundant/replaced columns ---
  select(-ADJINC, -HISP, -POBP, -state) |>

  # --- Ensure valid person weight ---
  filter(!is.na(PWGTP), PWGTP > 0)

#glimpse(pums_clean)
```


```{r}
#| label: eda-overview
#| echo: false

# --- Note ---
# after data pull and scrub in Python from the API
# the following was a proposed EDA method
# the group did chose to work in a different direction for EDA
# we have left if here for possible future use

library(tidyverse)
library(skimr)

# 1. overall summary
#skim(pums_clean)
```

```{r}
#| label: eda-missingness
#| echo: false
```

```{r}
#| label: eda-income-distributions
#| echo: false

# Wages among earners only

# Log wages

# Total personal income
```

```{r}
#| label: eda-outcome-summaries
#| echo: false

# Q1/Q3: wage statistics by key groups

# Q2: health insurance coverage rate

# Q2: uninsured rate by citizenship
```

```{r}
#| label: eda-categorical-distributions
#| echo: false
```

```{r}
#| label: eda-continuous-distributions
#| echo: false
```

```{r}
#| label: eda-correlations
#| echo: false

# --- End EDA proposal ---

library(corrr)
```

## Exploratory Data Analysis

We begin by exploring the relationship between income and our key predictors: age, education, gender, race, location and number of household members. 

```{r}
#| label: eda-histograms
#| echo: false
hist(pums_clean$PINCP)
hist(log(pums_clean$PINCP))
```

```{r}
#| label: eda-incomevage
#| echo: false
ggplot(pums_clean, aes(x = AGEP, y = PINCP)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(title = "Income vs Age")
```

The above summary statistics indicate that income (PINCP) is highly right-skewed, with a small number of individuals earning substantially more than the median. Because of this skewness, we will consider applying a log transformation to the income response when evaluating model fit for the final report. The scatterplot of income versus age suggests a nonlinear relationship: income tends to increase with age early in life, plateau in middle age, and decline slightly at older ages. This pattern suggests the inclusion of a quadratic age term in the regression model.

```{r}
#| label: eda-incomeved
#| echo: false
ggplot(pums_clean, aes(x = SCHL, y = PINCP)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(title = "Income vs Education", x = "Years of School (Education)", y = "Income")
  
```

```{r}
#| label: eda-incomevgender
#| echo: false
ggplot(pums_clean, aes(x = factor(SEX), y = PINCP)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 200000)) +
  scale_x_discrete(labels = c("Male", "Female")) +
  labs(
    title = "Income by Gender",
    x = "Gender",
    y = "Income"
  ) +
  theme_minimal()
```

```{r}
#| label: eda-incomevrace
#| echo: false
ggplot(pums_clean, aes(x = factor(RAC1P), y = PINCP)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 200000)) +
  labs(
    title = "Income by Race",
    x = "Race",
    y = "Income"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

As shown above, education shows a strong positive association with income, with higher educational attainment corresponding to higher earnings. Boxplots of income by gender and race reveal noticeable differences in median income across groups, suggesting these variables should be included as categorical predictors. Overall, the exploratory analysis indicates that income is associated with multiple demographic and socioeconomic variables, and that nonlinear effects (particularly for age) may be important.Overall, the exploratory analysis indicates that income is associated with multiple demographic and socioeconomic variables, and that nonlinear effects (particularly for age) may be important.

## Modeling: Preliminary Models

Based on our analysis of the data, we fit multiple linear regression models to assess how well income can be predicted from the selected variables. The initial full model is:

Income∼Age+Age^2+Education+Gender+Race+Birthplace+Household members

```{r}
#| label: model-1-2-3
#| echo: false
# Urban/Rural is hard to codify in the data, so it may be best to not include it.

library(car)

model1 <- lm(PINCP~AGEP+I(AGEP^2)+SCHL+factor(SEX)+factor(RAC1P)+factor(POBP_binary) + NP, data=pums_clean)
summary(model1)

model2 <- lm(PINCP~AGEP+AGEP^2+SCHL+factor(SEX)+factor(RAC1P), data=pums_clean)
summary(model2)

vif(model1)

model3 <- lm(PINCP~AGEP+SCHL+factor(SEX)+factor(RAC1P), data=pums_clean)
summary(model2)

anova(model2, model3)
```

Income is modeled as a continuous response, and predictors include both continuous variables (age, education, household members) and categorical variables (gender, race, birthplace). A quadratic term for age is included to capture the nonlinear relationship observed in the exploratory analysis.

A reduced model excluding birthplace and household members is also considered due to weak initial evidence of its importance:

Income∼Age+Age^2+Education+Gender+Race

## Model Checking and Selection

```{r}
#| label: model-plots
#| echo: false
plot(model2, which = 1)
plot(model2, which = 2)

#model_log <- lm(log(PINCP + 1) ~ AGEP + I(AGEP^2) + SCHL + factor(SEX) + factor(RAC1P), data = pums_clean)

#lot(model_log, which = 1)
#plot(model_log, which = 2)
```

Model diagnostics were conducted to assess the validity of the linear regression assumptions. Residual plots indicated non-constant variance and right-skewness, which is consistent with the skewed distribution of income. This suggests that a log transformation of income may improve model fit, although the untransformed model is retained for interpretability.

Multicollinearity was assessed using variance inflation factors (VIF). All predictors showed low VIF values (near 1), except for age and age squared, which exhibited moderate collinearity. This is expected due to the polynomial relationship and does not invalidate the model. Centering age can reduce this collinearity but does not change model fit.

Model selection was performed using both hypothesis testing and goodness-of-fit measures. An ANOVA comparison between models with and without the quadratic age term showed that including age squared significantly improves model fit (p < 0.001). In contrast, the inclusion of location (birthplace) did not significantly improve the model and resulted in only a negligible increase in R². Therefore, location was removed from the final model.


The final selected model is:

Income∼Age+Age^2+Education+Gender+Race

## Conclusions

Our analysis shows that income can be partially predicted using age, education, gender, and race. Education is the strongest predictor, with higher levels of education associated with substantially higher income. Age has a nonlinear relationship with income, with earnings increasing early in life, peaking in mid-career, and declining slightly thereafter. Gender and race also show statistically significant associations with income, even after controlling for other variables.

Despite these significant relationships, the overall explanatory power of the model is modest (R² = 0.12), indicating that we may need to consider other variables as determinants of income. Going forward there are additional factors to consider. One would be exploring additional variables for positive associates with income that could be added to the model. Another option is testing interaction terms. We could also consider whether gender and race are impactful enough that we should really be developing separate models in order to accurately capture the full impact these categorical variables have on all other aspects. 


## Citations

1. U.S. Census Bureau. (2026). 2020–2024 American Community Survey 5-year Public Use Microdata Sample (PUMS). U.S. Department of Commerce. https://www.census.gov/programs-surveys/acs/microdata.html

2. Mason, H., & Wiggins, C. (2010). A Taxonomy of Data Science. (Archived manuscript / teaching document). Accessed on 4/10/2026 https://introdatasci.dlilab.com/pdf/A_Taxonomy_of_Data_Science.pdf

## Appendix

```{r appendix-collect, include=FALSE}
all_chunks <- setdiff(knitr::all_labels(), c("appendix-collect", "appendix"))
```

```{r appendix, ref.label=all_chunks}
#| echo: true
#| eval: false

```

## Question 3

Our third question for analysis was whether income can be predicted from commute time, location, and travel ability. To do this, we will want to design a model to predict income and test it for prediction accuracy. 


To begin with we need to further explore the data with the context of variables as they relate to travel/commute. Below is the graph of reported income vs commute time.

### Exploration Data Analysis

```{r}
#| label: eda-incomevcommutetime
#| echo: false
#| warning: false
ggplot(pums_clean, aes(x = JWMNP, y = PINCP)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(title = "Income vs Commute Time")
  
```
In the above graph comparing commute time(JWMNP) and income(PINCP) we see a sort of conflicting trend in the data. The maximums appears to decrease as commutes increase, but there also a significant cluster of people with shorter commutes that make less money. There is also some complication in the data as many people appear to have rounded their answer to the nearest 5 minutes, but that is not the case for everyone.


```{r}
#| label: eda-incomebytraveltype
#| echo: false
#| warning: false
ggplot(pums_clean, aes(x = JWMNP, y = PINCP)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(title = "Income vs Commute Time by Travel Type") + 
  facet_grid(rows = vars(JWTRNS))+
  theme(strip.text.y = element_text(angle = 0))
```
The above graph is a repeat of the previous, but broken down by mode of transportation (JWTRNS). This breakdown offers a couple of useful insights. One is that in general, there appears to be a slight decline as  the length of commute by any method increases, and the second is that travel is overwhelmingly done by car.
  
```{r}
#| label: eda-commutetype
  ggplot(pums_clean, aes(x = JWTRNS)) +
  geom_bar(alpha = 0.2) +
  labs(title = "Commute Type Usage") +
  theme(axis.text.x = element_text(angle = 45, hjust=1))
```
This is further emphasized in this bar chart. 
  
```{r}
#| label: eda-incomebyarea
  


ggplot(pums_true, aes(x = factor(PUMA), y = PINCP)) +
  geom_boxplot() +
  coord_cartesian(ylim = c(0, 100000)) +
  labs(
    title = "Income by Area",
    x = "Area",
    y = "Income"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```
Finally, we comparing income against the geographic area code, which does show a lot of variation by breakdown. In the initial goal of this project, we wanted the comparison to be city vs suburban vs rural, but the data doesn't have a clear way to determine that, and the 100,000 person areas in this data cover multiple living environments.

After going through the exploratory variables, we begin building the model. First we filter out rows with missing values relating to income or commute method.



```{r}
#| label: q3-model-prep
#| echo: false

 pums_true <- pums_clean |> 
    filter(is.na(PINCP) == FALSE) |>
    filter(is.na(JWMNP) == FALSE) |>
    filter(is.na(JWTRNS) == FALSE)

```

### Model fitting

Based on our exploratory analysis. The model we want to go with is: 
PINCP ~ JWMNP + VEH + factor(JWTRNS) + factor(PUMA), which is predicting income based on commute time, vehicle availability, commute vehicle, and area.

```{r}
#| label: q3-model-exploration
#| echo: false


commutemodel <- lm(PINCP ~ JWMNP + VEH + factor(JWTRNS) + factor(PUMA), 
  data = pums_clean)
```


### Model selection

```{r}

summary(commutemodel)
  
```
Based on the summary analysis of the model, every variable is statistically significant at p: 0.05 level (or at least some values of the categorical variables, even if not every value). Next we want to check the residuals.



```{r}
#| label: q3-model-exploration
#| echo: false
#| warning: false


  fit_q1_diag <- broom::augment(commutemodel, data = pums_true)
  qplot(.fitted, .resid, data = fit_q1_diag)

```
  In graphing the residuals we can see there is still a slight downward trend in the  data, and that there is maybe an subgroup in the data that is not fully accounted for. Now let us try testing our model.
  



```{r}
#| echo: false
#| message: false
  

  
  val1.errors <- rep(NA,400)
  #val2.errors <- rep(NA,400)

  

  for(i in 1:400){
  
    pums_test <- pums_true|>
      slice_sample(prop=0.1)
      
    pums_train<- pums_true |>
        anti_join(pums_test)
  
    pums_eval <- pums_test |> select(PINCP)
    pums_test <- pums_test |> select(-PINCP)
  
  
    model1 <- lm(PINCP ~ JWMNP + VEH + factor(JWTRNS) + factor(PUMA), 
        data = pums_train)
    #model2 <- lm(PINCP ~ JWMNP, data = pums_train)
    
    predictions <- predict(model1, pums_test)
    #predictions2 <- predict(model2, pums_test)
  
    val1.errors[i] <- mean((pums_eval$PINCP-predictions))
    #val2.errors[i] <- mean((pums_eval$PINCP-predictions2))
    
  }
  #val1.errors  
  
  #mean(val2.errors)


  
```

To get an accurate sense of how well the model predicts, we are going to fit the model on a randomized 90% of the dataset. We will then ask it to predict the income for the other ten percent, then compare it to the actual value for that observation. This process is repeated multiple times with a fresh model so we can get a sense of the general predictive accuracy.

### model inference

```{r}
    mean(val1.errors)
    qplot(val1.errors, bins = 50 )
    
  
```
After running the testing for a few hundred rounds, we get a general sense of accuracy of the model. Our model isn't 100% accurate toward predicting income, on average it underpredicts the income but is within a hundred dollars. However, any specific training of the model can vary wildly, being withing about 2 grand on average.

Overall we would say this is a fairly accurate predictor for a four variable model. There is a lot of other angles to approach with a question specifically tailored around how home neighborhood and travel availability relates to income, but that is a question that would require additional information not collected in this dataset



# Obstacles

There were a few obstacles we ran into on question 3. One was how best to evaluate predictive accuracy. We knew it needed to be tested across multiple iterations to get an general accuracy, but I also wanted to show the variance between each round. Ultimately we settled on giving the overall mean prediction accuracy, as well as a histogram to demonstrate the spread of predictions. The other issue we faced was in adapting the question 3 "rural" value. As previously mentioned we tried to find a solution to this issue but none of the information within this dataset seemed to fulfill. The area zones are all 100,000 people at least, even if uneven numbers of people were surveyed from each, and there was no variables directly measuring population density or that could be used to determine it. Ultimately we just used area zones as a separate predictive variable instead of specifically "rural/urban" comparison.

# Conclusions


