---
title: "Group 4 Project 1: Group Proposal"
author: Paul Anderson, Michael Barton, Kevin Kincade
format: pdf
---

```{r}
library(tidyverse)
```

# Observe

This analysis draws on the 2020–2024 American Community Survey (ACS) 5-Year Public Use Microdata Sample (PUMS) for Oregon, accessed via the U.S. Census Bureau's API. The ACS PUMS files contain individual-level records for a subsample of approximately five percent of the U.S. population, with disclosure protections applied to prevent identification of specific individuals or households. The 5-year sample pools five consecutive years of survey data, which may assist with our ability to evaluate and produce analysis when considering relatively small subgroups in state-level (Oregon) data. Records are drawn at the Public Use Microdata System (PUMS) level API, the most granular geography available in the PUMS. The dataset used here includes person-level records and covers a range of demographic, socioeconomic, labor market, and health variables. All income and earnings variables are adjusted to constant dollars using the Census Bureau's provided adjustment factor (ADJINC), and all estimates should be computed using the person weight (PWGTP) to produce population-representative results. (1)

For this report we use the OSEMN model for collaborative data science as defined by Mason and Wiggins. (2)

```{r}
#| label: install-deps
#| include: false
# reticulate::virtualenv_create("r-reticulate")
# reticulate::virtualenv_install("r-reticulate", c("requests", "pandas"))
```

```{r}
#| label: add-reticulate
#| include: false
# file.edit("~/.Rprofile")
# add in this 
# Sys.setenv(RETICULATE_PYTHON_ENV = "r-reticulate")
```

```{r}
#| label: optional-pyrestart
#| include: false
# run the following restart the python session if needed
# reticulate::py_run_string("import gc; gc.collect()")
```

```{python}
# Scrub
#| label: fetch-pums
#| echo: false
#| cache: false

import requests
import pandas as pd
from pathlib import Path

API_KEY = "a8f34453c39e419470f405353250f662a508d821"
YEAR = 2024
STATE = "41"
CACHE_PATH = Path("data/pums_oregon_2024.csv")

variables = [
    # Outcomes
    "WAGP", "PINCP", "PERNP", "POVPIP", "HICOV", "ESR",
    # Core demographics
    "AGEP", "SEX", "RAC1P", "HISP", "CIT", "YOEP", "MAR", "RELSHIPP",
    "POBP",                                                       # added POBP
    # Education
    "SCHL", "FOD1P", "SCH",
    # Labor market
    "COW", "WKHP", "WKWN", "NAICSP", "OCCP", "WRK", "JWMNP", "JWTRNS", # added
    # Geography
    "PUMA", "MIG", "MIGSP", "POWSP",
    # Disability & health
    "DIS", "DPHY", "DREM", "DEAR", "DEYE",
    # Household context
    "HINCP", "HHT", "TEN", "VEH", "NRC",                            # added NRC
    # Income components
    "RETP", "SSP", "SSIP", "PAP", "SEMP",
    # Weights & adjustments
    "PWGTP", "ADJINC","NP",
]

if CACHE_PATH.exists():
    print(f"Loading from local cache: {CACHE_PATH}")
    pums = pd.read_csv(CACHE_PATH, low_memory=False)
    print(f"Loaded: {len(pums):,} rows, {pums.shape[1]} columns")
else:
    print(f"Cache not found — fetching from Census API...")
    CACHE_PATH.parent.mkdir(parents=True, exist_ok=True)
    url = (
        f"https://api.census.gov/data/{YEAR}/acs/acs5/pums"
        f"?get={','.join(variables)}"
        f"&for=state:{STATE}"
        f"&key={API_KEY}"
    )
    response = requests.get(url, timeout=60)
    print(f"Status code: {response.status_code}")
    if response.status_code == 200:
        data = response.json()
        pums = pd.DataFrame(data[1:], columns=data[0])
        pums.to_csv(CACHE_PATH, index=False)
        print(f"Saved to {CACHE_PATH}: {len(pums):,} rows, {pums.shape[1]} columns")
    else:
        print(f"Error: {response.text[:500]}")
```


# Scrub
```{python}
#| label: fetch-pums
#| echo: false
#| cache: false

import requests
import pandas as pd
from pathlib import Path

API_KEY = "a8f34453c39e419470f405353250f662a508d821"
YEAR = 2024
STATE = "41"
CACHE_PATH = Path("data/pums_oregon_2024.csv")

variables = [
    # Outcomes
    "WAGP", "PINCP", "PERNP", "POVPIP", "HICOV", "ESR",
    # Core demographics
    "AGEP", "SEX", "RAC1P", "HISP", "CIT", "YOEP", "MAR", "RELSHIPP",
    "POBP",                                                       # added POBP
    # Education
    "SCHL", "FOD1P", "SCH",
    # Labor market
    "COW", "WKHP", "WKWN", "NAICSP", "OCCP", "WRK", "JWMNP", "JWTRNS", # added
    # Geography
    "PUMA", "MIG", "MIGSP", "POWSP",
    # Disability & health
    "DIS", "DPHY", "DREM", "DEAR", "DEYE",
    # Household context
    "HINCP", "HHT", "TEN", "VEH", "NRC",                            # added NRC
    # Income components
    "RETP", "SSP", "SSIP", "PAP", "SEMP",
    # Weights & adjustments
    "PWGTP", "ADJINC","MET2013",
]

if CACHE_PATH.exists():
    print(f"Loading from local cache: {CACHE_PATH}")
    pums = pd.read_csv(CACHE_PATH, low_memory=False)
    print(f"Loaded: {len(pums):,} rows, {pums.shape[1]} columns")
else:
    print(f"Cache not found — fetching from Census API...")
    CACHE_PATH.parent.mkdir(parents=True, exist_ok=True)
    url = (
        f"https://api.census.gov/data/{YEAR}/acs/acs5/pums"
        f"?get={','.join(variables)}"
        f"&for=state:{STATE}"
        f"&key={API_KEY}"
    )
    response = requests.get(url, timeout=60)
    print(f"Status code: {response.status_code}")
    if response.status_code == 200:
        data = response.json()
        pums = pd.DataFrame(data[1:], columns=data[0])
        pums.to_csv(CACHE_PATH, index=False)
        print(f"Saved to {CACHE_PATH}: {len(pums):,} rows, {pums.shape[1]} columns")
    else:
        print(f"Error: {response.text[:500]}")
```

```{r}
#| label: load-pums
#| echo: false

pums <- read_csv("data/pums_oregon_2024.csv", show_col_types = FALSE)

glimpse(pums)
```

```{r}
#| label: scrub-pums
#| echo: false
#| cache: true

library(tidyverse)

pums_clean <- pums |>

  # --- Remove group quarters records ---
  filter(HINCP != -60000) |>

  # --- Apply income adjustment factor ---
  mutate(
    across(c(WAGP, PINCP, PERNP, HINCP, RETP, SSP, SSIP, PAP, SEMP),
           ~ .x * ADJINC)
  ) |>

  # --- Recode all N/A sentinels to NA ---
  mutate(
    # Income vars: age-based N/A
    WAGP   = na_if(WAGP,  -1 * ADJINC),
    PERNP  = na_if(PERNP, -10001 * ADJINC),
    PINCP  = na_if(PINCP, -19999 * ADJINC),
    RETP   = na_if(RETP,  -1 * ADJINC),
    SSP    = na_if(SSP,   -1 * ADJINC),
    SSIP   = na_if(SSIP,  -1 * ADJINC),
    PAP    = na_if(PAP,   -1 * ADJINC),
    SEMP   = na_if(SEMP,  -10001 * ADJINC),
    # Labor market: 0 = N/A (under 16 or did not work)
    WKHP   = na_if(WKHP, 0),
    WKWN   = na_if(WKWN, 0),
    JWMNP  = na_if(JWMNP, 0),
    # Other sentinels
    POVPIP = na_if(POVPIP, -1),
    ESR    = na_if(ESR, 0),
    YOEP   = na_if(YOEP, 1937),
    HHT    = na_if(HHT, 0),
    TEN    = na_if(TEN, 0),
    VEH    = na_if(VEH, -1),
    NRC    = na_if(NRC, -1),
    DPHY   = na_if(DPHY, 0),
    DREM   = na_if(DREM, 0),
    NP     = na_if(NP, 0),
    # Labor class and work status: 0 = N/A
    COW    = na_if(COW, 0),
    WRK    = na_if(WRK, 0),
  ) |>

  # --- Recode binary vars to logical (1=Yes, 2=No) ---
  mutate(
    across(c(DPHY, DREM, DEAR, DEYE, DIS), ~ .x == 1),
    HICOV = HICOV == 1,
  ) |>

  # --- Recode categorical vars as factors with labels from metadata ---
  mutate(
    SEX = factor(SEX, levels = c(1, 2),
                 labels = c("Male", "Female")),

    RAC1P = factor(RAC1P, levels = 1:9,
                   labels = c("White alone", "Black or African American alone",
                              "American Indian alone", "Alaska Native alone",
                              "AIAN tribes specified", "Asian alone",
                              "Native Hawaiian and Other Pacific Islander alone",
                              "Some other race alone", "Two or More Races")),

    HISP_binary = factor(if_else(HISP == "01", "Not Hispanic", "Hispanic")),

    CIT = factor(CIT, levels = 1:5,
                 labels = c("Born in US", "Born in PR/territories",
                            "Born abroad of US citizen parent",
                            "Naturalized citizen", "Not a US citizen")),

    MAR = factor(MAR, levels = 1:5,
                 labels = c("Married", "Widowed", "Divorced",
                            "Separated", "Never married")),

    ESR = factor(ESR, levels = 1:6,
                 labels = c("Civilian employed at work",
                            "Civilian employed not at work",
                            "Unemployed",
                            "Armed Forces at work",
                            "Armed Forces not at work",
                            "Not in labor force")),

    SCH = factor(SCH, levels = 1:3,
                 labels = c("Not enrolled", "Public school", "Private school")),

    COW = factor(COW, levels = 1:9,
                 labels = c("Private for-profit", "Private nonprofit",
                            "Local govt", "State govt", "Federal govt",
                            "Self-emp incorporated", "Self-emp not incorporated",
                            "Working without pay", "Unemployed last 5 years")),

    MIG = factor(MIG, levels = 1:3,
                 labels = c("Same house", "Outside US", "Different house in US")),

    HHT = factor(HHT, levels = 1:7,
                 labels = c("Married couple household",
                            "Other family: male householder no spouse",
                            "Other family: female householder no spouse",
                            "Nonfamily: male householder living alone",
                            "Nonfamily: male householder not living alone",
                            "Nonfamily: female householder living alone",
                            "Nonfamily: female householder not living alone")),

    TEN = factor(TEN, levels = 1:4,
                 labels = c("Owned with mortgage", "Owned free and clear",
                            "Rented", "Occupied without payment")),

    WRK = factor(WRK, levels = 1:2,
                 labels = c("Worked last week", "Did not work last week")),

    JWTRNS = factor(JWTRNS, levels = 0:12,
                    labels = c("N/A", "Car truck or van", "Bus",
                               "Subway or elevated rail",
                               "Long-distance train or commuter rail",
                               "Light rail streetcar or trolley",
                               "Ferryboat", "Taxi or ride-hailing",
                               "Motorcycle", "Bicycle", "Walked",
                               "Worked from home", "Other method")),

    POBP_binary = factor(case_when(
      as.numeric(POBP) <= 56  ~ "Born in US",
      as.numeric(POBP) == 72  ~ "Born in PR/territories",
      TRUE                    ~ "Foreign born"
    )),
  ) |>

  # --- Drop redundant/replaced columns ---
  select(-ADJINC, -HISP, -POBP, -state) |>

  # --- Ensure valid person weight ---
  filter(!is.na(PWGTP), PWGTP > 0)

#glimpse(pums_clean)
```
Data Cleaning Notes 2020–2024 ACS 5-Year PUMS (Oregon)
ACS PUMS uses numeric codes for missing or inapplicable values, so all recoding follows the official Census metadata.

Group quarters. Dropped records with HINCP = -60000 (e.g., prisons, dorms) since household variables don’t apply. Final sample: 197,991.

Income adjustment. Scaled all income variables using ADJINC (1.222017) to get constant dollars, then removed ADJINC.

Sentinel values. Converted all placeholder codes to NA. Income variables use age-based sentinels; work variables use 0 for non-workers/under 16. Other examples: POVPIP (-1), YOEP (1937 for non-immigrants), and some disability/household codes for inapplicable cases.

Binary recodes. Turned 1/2-coded variables (disability and insurance) into TRUE/FALSE.

Categoricals. Converted to labeled factors. Most drop “N/A” levels after cleaning, but commuting (JWTRNS) keeps a non-commuter category; ESR keeps NA for under 16.

Derived variables. Simplified HISP to Hispanic vs. not, and POBP to U.S., territories, or foreign-born. Dropped originals after.

Kept as-is. Industry, occupation, migration, etc. stay in raw form for later grouping. SCHL stays ordinal; PUMA is used as a geographic ID.



# Explore

Next steps, explore the data, number of missing variables, distributions, outcome summaries, categorical distributions, continuous distributions, correlations

```{r}
#| label: eda-overview
#| echo: false

library(tidyverse)
library(skimr)

# 1. overall summary
skim(pums_clean)
```

```{r}
#| label: eda-missingness
#| echo: false
```

```{r}
#| label: eda-income-distributions
#| echo: false

# Wages among earners only

# Log wages

# Total personal income
```

```{r}
#| label: eda-outcome-summaries
#| echo: false

# Q1/Q3: wage statistics by key groups

# Q2: health insurance coverage rate

# Q2: uninsured rate by citizenship
```

```{r}
#| label: eda-categorical-distributions
#| echo: false
```

```{r}
#| label: eda-continuous-distributions
#| echo: false
```

```{r}
#| label: eda-correlations
#| echo: false

library(corrr)
```

# Questions

Paul
What is the wage penalty (or premium) associated with disability status in Oregon, after controlling for education, occupation, hours worked, and demographics? Outcome: Wage penalty Predictors: Education, occupation, hours worked, demographics
What individual characteristics predict lacking health insurance coverage in Oregon, and has the coverage gap by citizenship status narrowed? Outcome: lack of health insurance Precitors: Income, education, household size, occupation, hours worked, citizenship status

Mike
- Can income be predicted from age, education, and location (rural vs urban)? Outcome: Income Predictors: Age Education Location
- What factors are associated with spending more than 30% of income on housing? (What factors contribute to household cost burden) Outcome: Spending more than 30% of income on housing T/F Predictors: Income, household size, education.
- How do age, education, hours worked, and occupation affect annual earnings? Outcome: Annual earnings Predictors: Age Education Hours Worked Occupation

Kevin
- can income be predicted from commute time (JWMNP), vehicle (VEH), and location
Outcome: Income Predictors based on travel arrangements (urban vs rural vs suburb) 
Outcome: Income Predictor: Commute Time, Vehicle, Location
- determining whether the effect of education on income has decreased over time
comparing different age demographics and seeing if the effect of education on income is different for different cohorts
Outcome: determining shifts in valuation of degrees over time wrt actual earnings
Outcome: Income Predictor: Age demographics, Education (Highest Degree Earned)

Question #1
Idea: Full model and reduced, run an ANOVA
Can income be predicted from age, education, and location (rural vs urban)? Outcome: Income Predictors: Age, Education, Location, Gender, Race, Birthplace, Family Size

```{r}
#lm(ADJINC~age+education+rural+gender+race+birthplace, data=pums_clean)
# Urban/Rural is hard to codify in the data, so it may be best to not include it.
model1 <- lm(PINCP~AGEP+I(AGEP^2)+SCHL+factor(SEX)+factor(RAC1P)+factor(POBP_binary) + NP, data=pums_clean)
summary(model1)


model2 <- lm(PINCP~AGEP+AGEP^2+SCHL+factor(SEX)+factor(RAC1P), data=pums_clean)
summary(model2)
```

```{r}
plot(model2, which = 1)
plot(model2, which = 2)

model_log <- lm(log(PINCP + 1) ~ AGEP + I(AGEP^2) + SCHL + factor(SEX) + factor(RAC1P), data = pums_clean)

plot(model_log, which = 1)
plot(model_log, which = 2)
```


```{r}
library(car)
vif(model1)


model3 <- lm(PINCP~AGEP+SCHL+factor(SEX)+factor(RAC1P), data=pums_clean)
summary(model2)

anova(model2, model3)
```


```{r}
ggplot(pums_clean, aes(x = AGEP, y = PINCP)) +
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess") +
  labs(title = "Income vs Age")
```



Question #2
What individual characteristics predict lacking health insurance coverage in Oregon, with additional aspect to Citizenship. Outcome: lack of health insurance Precitors: Income, education, household size, occupation, hours worked, citizenship status

Question #3
Can income be predicted from commute time (JWMNP), vehicle (VEH), and location
Outcome: Income Predictors based on travel arrangements (urban vs rural vs suburb)

# Model

# iNterpret

# Citations

1. U.S. Census Bureau. (2026). 2020–2024 American Community Survey 5-year Public Use Microdata Sample (PUMS). U.S. Department of Commerce. https://www.census.gov/programs-surveys/acs/microdata.html

2. Mason, H., & Wiggins, C. (2010). A Taxonomy of Data Science. (Archived manuscript / teaching document). Accessed on 4/10/2026 https://introdatasci.dlilab.com/pdf/A_Taxonomy_of_Data_Science.pdf